Dynein walks like an Imperial AT-ST

### 2018-08-16 papers/paper/paper.tex
Add experimental values to paper table

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & & \cite{burgess-paper}\\
$L_t$ & $\lt nm$ & & \cite{burgess-paper}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\
$D$ & 0.2 nm &  & \\

>>>>

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & & \\
$L_s$ & $\ls nm$ & 21nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
$L_t$ & $\lt nm$ & 23nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{burgess-paper}\\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{burgess-paper}\\
$\theta_t$ & $\eqt$ &  & \\
$R_t$ & $\radius_t$ & 8nm & \cite{burgess-paper}\\
$R_m$ & $\radius_m$ & 11nm & \cite{burgess-paper}\\
$R_b$ & $\radius_b$ & 3.5nm & \cite{burgess-paper}\\
